\begin{longtable}{@{\hskip0pt} p{8cm} | p{8cm} @{\hskip0pt}}
Cum invocárem exaudívit me Deus justítiæ \textbf{me}æ:~* in tribulatióne dila\textit{tás}\textit{ti} \textbf{mi}hi.
 & When I called upon him, the God of my justice heard me: * when I was in distress, thou hast enlarged me.
\\
Miserére \textbf{me}i,~* et exáudi orati\textit{ó}\textit{nem} \textbf{me}am.
 & Have mercy on me: * and hear my prayer.
\\
Fílii hóminum, úsquequo gravi \textbf{cor}de?~* ut quid dilígitis vanitátem et qu\'{\ae}ri\textit{tis} \textit{men}\textbf{dá}cium?
 & O ye sons of men, how long will you be dull of heart? * Why do you love vanity, and seek after lying?
\\
Et scitóte quóniam mirificávit Dóminus sanctum \textbf{su}um:~* Dóminus exáudiet me cum clamáve\textit{ro} \textit{ad} \textbf{e}um.
 & Know ye also that the Lord hath made his holy one wonderful: * the Lord will hear me when I shall cry unto him.
\\
Irascímini, et nolíte peccáre:~\GreDagger\ quæ dícitis in córdibus \textbf{ves}tris,~* in cubílibus vestris \textit{com}\textit{pun}\textbf{gí}mini.
 & Be ye angry, and sin not: * the things you say in your hearts, be sorry for them upon your beds.
\\
Sacrificáte sacrifícium justítiæ,~\GreDagger\ et speráte in \textbf{Dó}mino.~* Multi dicunt: quis osténdit \textit{no}\textit{bis} \textbf{bo}na?
 & Offer up the sacrifice of justice, and trust in the Lord: * many say, Who sheweth us good things?
\\
Signátum est super nos lumen vultus tui, \textbf{Dó}mine:~* dedísti lætítiam in \textit{cor}\textit{de} \textbf{me}o.
 & The light of thy countenance, O Lord, is signed upon us: * thou hast given gladness in my heart.
\\
A fructu fruménti, vini et ólei \textbf{su}i~* mul\textit{ti}\textit{pli}\textbf{cá}ti sunt.
 & By the fruit of their corn, their wine, and oil, * they are multiplied.
\\
In pace in id\textbf{íp}sum~* dórmiam et \textit{re}\textit{qui}\textbf{és}cam;
 & In peace in the selfsame * I will sleep, and I will rest:
\\
Quóniam tu, Dómine, singuláriter \textbf{in} spe~* con\textit{sti}\textit{tu}\textbf{ís}ti me.
 & For thou, O Lord, singularly * hast settled me in hope.
\\
Glória Patri, et \textbf{Fí}lio,~* et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
 & Glory be to the Father, and to the Son, * and to the Holy Ghost.
\\
Sicut erat in princípio, et nunc, et \textbf{sem}per,~* et in s\'{\ae}cula sæcu\textit{ló}\textit{rum}. \textbf{A}men. & As it was in the beginning, is now, * and ever shall be, world without end. Amen.\\
\end{longtable}