\begin{longtable}{@{\hskip0pt} p{8cm} | p{8cm} @{\hskip0pt}}
Qui hábitat in adjutório Al\textbf{tís}simi,~* in protectióne Dei cæli \textit{com}\textit{mo}\textbf{rá}bitur.
 & He that dwelleth in the aid of the most High, * shall abide under the protection of the God of Jacob.
\\
Dicet Dómino: Suscéptor meus es tu, et refúgium \textbf{me}um:~* Deus meus sperá\textit{bo} \textit{in} \textbf{e}um.
 & He shall say to the Lord: Thou art my protector, and my refuge: * my God, in him will I trust.
\\
Quóniam ipse liberávit me de láqueo ve\textbf{nán}tium,~* et a \textit{ver}\textit{bo} \textbf{ás}pero.
 & For he hath delivered me from the snare of the hunters: * and from the sharp word.
\\
Scápulis suis obumbrábit \textbf{ti}bi:~* et sub pennis e\textit{jus} \textit{spe}\textbf{rá}bis.
 & He will overshadow thee with his shoulders: * and under his wings thou shalt trust.
\\
Scuto circúmdabit te véritas \textbf{e}jus:~* non timébis a timó\textit{re} \textit{noc}\textbf{túr}no.
 & His truth shall compass thee with a shield: * thou shalt not be afraid of the terror of the night.
\\
A sagítta volánte in die,~\GreDagger\ a negótio perambulánte in \textbf{té}nebris:~* ab incúrsu et dæmónio me\textit{ri}\textit{di}\textbf{á}no.
 & Of the arrow that flieth in the day, of the business that walketh about in the dark: * of invasion, or of the noonday devil.
\\
Cadent a látere tuo mille,~\GreDagger\ et decem míllia a dextris \textbf{tu}is:~* ad te autem non ap\textit{pro}\textit{pin}\textbf{quá}bit.
 & A thousand shall fall at thy side, and ten thousand at thy right hand: * but it shall not come nigh thee.
\\
Verúmtamen óculis tuis conside\textbf{rá}bis:~* et retributiónem peccató\textit{rum} \textit{vi}\textbf{dé}bis.
 & But thou shalt consider with thy eyes: * and shalt see the reward of the wicked.
\\
Quóniam tu es, Dómine, spes \textbf{me}a:~* Altíssimum posuísti refú\textit{gi}\textit{um} \textbf{tu}um.
 & Because thou, O Lord, art my hope: * thou hast made the most High thy refuge.
\\
Non accédet ad te \textbf{ma}lum:~* et flagéllum non appropinquábit taberná\textit{cu}\textit{lo} \textbf{tu}o.
 & There shall no evil come to thee: * nor shall the scourge come near thy dwelling.
\\
Quóniam Angelis suis mandávit \textbf{de} te:~* ut custódiant te in ómnibus \textit{vi}\textit{is} \textbf{tu}is.
 & For he hath given his angels charge over thee; * to keep thee in all thy ways.
\\
In mánibus por\textbf{tá}bunt te:~* ne forte offéndas ad lápidem \textit{pe}\textit{dem} \textbf{tu}um.
 & In their hands they shall bear thee up: * lest thou dash thy foot against a stone.
\\
Super áspidem et basilíscum ambu\textbf{lá}bis:~* et conculcábis leónem \textit{et} \textit{dra}\textbf{có}nem.
 & Thou shalt walk upon the asp and the basilisk: * and thou shalt trample under foot the lion and the dragon.
\\
Quóniam in me sperávit, liberábo \textbf{e}um:~* prótegam eum quóniam cognóvit \textit{no}\textit{men} \textbf{me}um.
 & Because he hoped in me I will deliver him: * I will protect him because he hath known my name.
\\
Clamábit ad me, et ego exáudiam eum:~\GreDagger\ cum ipso sum in tribulati\textbf{ó}ne:~* erípiam eum et glorifi\textit{cá}\textit{bo} \textbf{e}um.
 & He shall cry to me, and I will hear him: * I am with him in tribulation, I will deliver him, and I will glorify him.
\\
Longitúdine diérum replébo \textbf{e}um:~* et osténdam illi salu\textit{tá}\textit{re} \textbf{me}um.
 & I will fill him with length of days; * and I will shew him my salvation.
\\
Glória Patri, et \textbf{Fí}lio,~* et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
 & Glory be to the Father, and to the Son, * and to the Holy Ghost.
\\
Sicut erat in princípio, et nunc, et \textbf{sem}per,~* et in s\'{\ae}cula sæcu\textit{ló}\textit{rum}. \textbf{A}men. & As it was in the beginning, is now, * and ever shall be, world without end. Amen.\\
\end{longtable}